Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-29 article.tex
Improve abstract

Transmembrane helices (TMHs) in the human proteome
are an overrepresented potential source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown if this same overrepresentation
also holds for the proteome of a pathogen.
Additionally, it is unknown if TMH-II is also likelier to present
TMHs than expected by chance. 
Lastly, if the immune system if more tailored to detect polypeptides
derived from TMHs, can we confirm this by detecting the evolutionary
conservation of this behavior?
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to polypeptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, this study shows that in the mutation rate in TMHs of a pathogen
is [lower/as much/higher] then expected just by chance, hinting at 
evolutionary [conservation/neutrality/disruptive selection].
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has left [a/no]
signal in the evolutionary history of the pathogen.

>>>>

Transmembrane helices (TMHs) in the human proteome
are an overrepresented potential source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown if the immune system is as able to detect those 
TMHs present in pathogens.
Additionally, it is unknown if TMH-II is also likelier to detect
human and pathogen TMHs than expected by chance.
It is unknown if natural selection is the cause that 
the immune system is more attentive for TMHs
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to polypeptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, we show that natural selection on TMHs is [strong enough/still too weak]
to detect.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.
